Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2013-12-27 paper.tex
Namecoin

Let's say Alice wants to register a domain name name. To achieve that, Alice needs money. The currency used in our model to buy domain names is called the Namecoin. Alice can exchange USDollars or Bitcoins to get those Namecoins.

>>>>

\subsubsection{From Bitcoin to Namecoin}

Now that we understand how blockchains work and why they are safe data-structures, let's now see how we can use them to square Zooko's triangle.

Namecoin is a bitcoin fork that was designed as a decentralized key-value store.

Putting information in the blockchain does cost a certain price hence

Let's say Alice wants to register a domain name name. To achieve that, Alice needs money, Namecoins.
